DNNNNR0: How to Avoid OOTA Without Really Trying

### 2025-03-27 paper/ootavacuous.tex
ootavacuous: Distinguish between syntactic and semantic dependencies
But no separate section, not yet, anyway.  We already noted carelessness
on the part of others ("Some discussions of semantic dependencies assume
that they are strictly functions of the source code.")

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Here we consider some of the complexities inherent to semantic
dependencies.

@@

Some discussions of semantic dependencies assume that they
are strictly functions of the source code.
Although there are ways of making this work, many instances of
semantic dependency must be considered functions of particular executions.
Consider for example:
\begin{quote}
\begin{verbatim}
x = y * z;
\end{verbatim}
\end{quote}

>>>>

Here we consider some of the complexities inherent to semantic
dependencies.
It is important to distinguish semantic dependencies from syntactic
dependencies.
Although every semantic dependency is also a syntactic dependency, many
syntactic dependencies can be optimized (or ``broken''), as will be seen
in the following sections.
Such syntactic dependencies are not semantic dependencies.

@@

Some discussions of semantic dependencies assume that they
are strictly functions of the source code.
This assumption is not always valid, in fact, we will see that many
instances of semantic dependency must be considered functions of
particular executions.
Consider for example:
\begin{quote}
\begin{verbatim}
x = y * z;
\end{verbatim}
\end{quote}
